A Study of Common Bug Fix Patterns in Rust \thanks{Competing Interests: We have no competing interests and are funded by a Discovery Grant from Canada's Natural Science and Engineering Research Council.}

### 2023-06-14 methodology.tex
reword scope

\paragraph{Example: computing fixed-sized vectors.} Figure~\ref{fig:essence} depicts the fixed-sized vectors, as described in this subsection, for the change from Figure~\ref{fig:extraction}. We have omitted scope information from this Figure for space reasons; the relevant scope is \verb+ItemFn+, indicating that these non-terminals occur within a function. It also depicts the essence of change, to be described immediately below.

@@

    \caption{\label{fig:essence}Multiplying the number of occurrences of items observed in the tree by their respective weights results in the essence of change, visualized with a circle pack figure at bottom right. Scope information (ItemFn) omitted from column headings for space purposes.}
\end{figure}

>>>>

\paragraph{Example: computing fixed-sized vectors.} Figure~\ref{fig:essence} depicts the fixed-sized vectors, as described in this subsection, for the change from Figure~\ref{fig:extraction}. All of the columns in this vector belong to scope \verb+ItemFn+---that is, these non-terminals occur within a function. The Figure also depicts the essence of change, to be described immediately below.

@@

    \caption{\label{fig:essence}Multiplying the number of occurrences of items observed in the tree by their respective weights results in the essence of change, visualized with a circle pack figure at bottom right. All non terminals here occur within scope {\texttt ItemFn}.}
\end{figure}
